[dcpo_demsupport]

### 2020-08-28 paper/dcpo_demsupport.Rmd
starting APSR analysis

```{r claassen-replication}
# Data input ----

@@

save(df_result_cls, file = here::here("output", "estimates_cls.RDS"))
```

```{r dcpo-point}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))

@@

df_dcpoMean <- df_dcpoMean %>% 
  left_join(df_controls, by = c("country", "year")) %>% 
  mutate(theta_dem = theta * regime,
         theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))

@@

df_result_dcpoMean <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = df_dcpoMean)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

save(df_result_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
```

```{r dcpo-uncertainty, eval = FALSE}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

load(here::here("output", "estimates_cls.RDS"))
load(here::here("output", "estimates_dcpoMean.RDS"))
load(here::here("output", "estimates_dcpo.RDS"))

@@

>>>>

```{r claassenAJPS}
# Data input ----

@@

save(df_result_cls, file = here::here("output", "estimates_clsAJPS.RDS"))
```

```{r dcpoPointAJPS}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))

@@

df_dcpoMeanAJPS <- df_dcpoMean %>% 
  left_join(df_controls, by = c("country", "year")) %>% 
  mutate(theta_dem = theta * regime,
         theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))

@@

df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

```{r dcpoUncertaintyAJPS, eval = FALSE}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}

load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
load(here::here("output", "estimates_dcpo.RDS"))

@@

```{r visualizedUncertain, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}

```{r claassenAPSR}
load("../data/dem_mood_apsr.RData")
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

mods <- vector(mode = "list")

mods[[1]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
  sd.plm,
  model = "pooling"
)
mods[[2]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
  sd.plm,
  model = "pooling"
)

vcovHC_se <-  function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

df_result_clsAPSR <- map(mods, function(aMod){
  tidy(aMod) %>%
    mutate(std.error = vcovHC_se(aMod))
})

save(df_result_clsAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
```

```{r dcpoPointAPSR}
df_controls <- read_csv(here::here("data", "APSRctlv.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"))

df_dcpoMeanAPSR <- df_dcpoMean %>% 
  left_join(df_controls, by = c("country", "year")) %>% 
  plm::pdata.frame(index = c("country", "year"))

mods <- vector(mode = "list")
mods[[1]] <-
  plm(
    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
    data = df_dcpoMeanAPSR,
    model = "pooling"
  )

mods[[2]] <-
  plm(
    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
    data = df_dcpoMeanAPSR,
    model = "pooling"
  )

df_result_dcpoMeanAPSR <- map(mods, function(aMod){
  aMod %>% 
    tidy %>%
    mutate(std.error = vcovHC_se(aMod))
})

save(df_result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
```

```{r dcpoUncertaintyAPSR, eval = FALSE}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

estimate_dcpo <- function(aDataset) {

    result_dcpo_1k <- vector(mode = "list")

    result_dcpo_1k[[1]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1), model = "pooling", data = aDataset)
    result_dcpo_1k[[2]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1), model = "pooling", data = aDataset)

    result_vars_dcpo_1k <- map(result_dcpo_1k, function(aFit){
      mitools::MIextract(aFit, fun = vcovHC_se)
    })

    result_betas_dcpo_1k <- map(result_dcpo_1k, function(aFit){
      mitools::MIextract(aFit, fun = coef)
    })

  df_result_dcpo <- map2(result_vars_dcpo_1k, result_betas_dcpo_1k, function(aVar, aBeta){
    summary(
      mitools::MIcombine(results = aBeta, variance = aVar)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
  })
}

df_result_dcpoAPSR <- map(df_dcpo, estimate_dcpo)

save(df_result_dcpoAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
```

```{r visualizedMood, fig.cap= "Effects of Democracy on Change in Mood"}

load(here::here("output", "estimates_clsAPSR.RDS"))
load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))
load(here::here("output", "estimates_dcpoAPSR.RDS"))

df_plot <- df_result_clsAPSR[[1]] %>% 
  mutate(model = "Claassen 2020")

df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)"),
    time = 2)
  )

plot_clsVsDCPO <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Democracy Mood")+
  theme(legend.position = "none")

df_plot <- df_result_clsAPSR[[2]] %>% 
  mutate(model = "Claassen 2020")

df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t−1)",
      "Corruption\n (Difference)",
      "Corruption\n (t−1)"
      ),time = 2)
  )

plot_clsVsDCPO2 <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Democracy Mood")+
  theme(legend.position = "none")
